---
output: github_document
---

<!-- 
README.md is generated from README.Rmd. Please edit that file
#knitr::knit("README.Rmd") 
rmarkdown::render("README.Rmd") 
maybe clear cache before
-->


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/REddyProcNCDF)](http://cran.r-project.org/package=REddyProcNCDF)
[![Travis-CI Build Status](https://travis-ci.org/bgctw/REddyProcNCDF.svg?branch=master)](https://travis-ci.org/bgctw/REddyProcNCDF)


## Overview

This is an extension of the 
[`REddyProc` package](https://github.com/bgctw/REddyProc), 
which supports processing (half)hourly data from Eddy-Covariance sensors.

It adds functionality of reading half-hourly Net Ecosystem Exchange (NEE) 
data from NetCDF files.

## Installation
### NetCDF system libraries
Reading NetCDF files requires several system libraries to be installed.

Debian based OS users (Ubuntu, Docker): do from a shell:
```
sudo apt-get update
sudo apt-get install libssl-dev
sudo apt-get install libnetcdf-dev
sudo apt-get install libudunits2-dev
```

Windows users, see [ncdf home page](http://cirrus.ucsd.edu/~pierce/ncdf/)

Mac users: 

### R-packages
```{r, eval = FALSE}
# Release stable version from CRAN
#not yet: install.packages("REddyProcNCDF")

# The development version from GitHub using devtools:
# install.packages("devtools")
install.packages("RNetCDF")
devtools::install_github("bgctw/REddyProcNCDF")
```

Alternatively to the RNetCDF package dependency, REddyProcNCDF also works if the
ncdf4 package has been installed.

## Usage

There is an example file acceseed from the REddyProc repository that
stores half-hourly Net-Ecosystem-Exchange (NEE) data, that is read and displayed.


```{r example, echo=TRUE}
library(REddyProcNCDF)
?REddyProcNCDF

#+++ Input data from NetCDF file (example needs to be downloaded)
examplePath <- getExamplePath('Example_DE-Tha.1996.1998.hourly_selVars.nc'
                              , isTryDownload = TRUE)
if (length(examplePath)) {
  EddyData.F <- fLoadFluxNCIntoDataframe(c('NEE', 'Rg', 'NEE_f'), examplePath)
} else {
  stop(
      "Could not find example text data file."
      ," In order to execute this example code,"
      ," please, allow downloading it from github. " 
      ," Type '?getExamplePath' for more information.")
}
head(EddyData.F)
```

