---
output: github_document
---

<!-- 
README.md is generated from README.Rmd. Please edit that file
#knitr::knit("README.Rmd") 
rmarkdown::render("README.Rmd") 
maybe clear cache before
-->


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/REddyProcNCDF)](http://cran.r-project.org/package=REddyProcNCDF)
[![Travis-CI Build Status](https://travis-ci.org/bgctw/REddyProcNCDF.svg?branch=master)](https://travis-ci.org/bgctw/REddyProcNCDF)


## Overview

This is an extension of the 
[`REddyProc` package](https://github.com/bgctw/REddyProc), 
which supports processing (half)hourly data from Eddy-Covariance sensors.

It adds functionality of reading half-hourly Net Ecosystem Exchange (NEE) 
data from NetCDF files.

## Installation
### NetCDF system libraries
Reading NetCDF files requires several system libraries to be installed.

Debian based OS users (Ubuntu, Docker): do from a shell:
```
sudo apt-get update
sudo apt-get install libnetcdf-dev
sudo apt-get install libudunits2-dev
```

Windows users, see [ncdf home page](http://cirrus.ucsd.edu/~pierce/ncdf/)

Mac users: TODO 

### R-packages
```{r, eval = FALSE}
# Release stable version from CRAN
#not yet: install.packages("REddyProcNCDF")

# The development version from GitHub using devtools:
# install.packages("devtools")
install.packages("RNetCDF")
devtools::install_github("bgctw/REddyProcNCDF")
```

Alternatively to the RNetCDF package dependency, REddyProcNCDF also works if the
ncdf4 package has been installed.

## Usage

There is an example file acceseed from the REddyProc repository that
stores half-hourly Net-Ecosystem-Exchange (NEE) data, that is read and displayed.


```{r example, echo=TRUE}
library(REddyProcNCDF)
?REddyProcNCDF

examplePath <- system.file(
  file.path('examples','Example_DE-Tha.1996.1998.hourly_selVars.nc')
  , package = "REddyProcNCDF")
EddyData.F <- fLoadFluxNCIntoDataframe(c('NEE', 'Rg', 'NEE_f'), examplePath)
head(EddyData.F)
# EddyData.F can now be used to initialize EddyProc R5 class 
```

